Towards Practical Probabilistic Programming

### 2018-10-31 abstract/paper.tex
in progress

\item The model code should be reusable between inference and
simulation. The code which is not required solely for inference
(simulation) should be written once for both inference of
parameters and use of the parameters in the host environment.
It should be possible to simulation outside the probabilistic
model without runtime or memory overhead imposed by inference
needs.
\end{enumerate}

>>>>

\item The model code should be reusable between inference and
simulation. The code which is not required solely for inference
should be written once for both inference of parameters and use
of the parameters in the host environment.  It should be
possible to run simulation outside the probabilistic model without
runtime or memory overhead imposed by inference needs.
\end{enumerate}
